Approximation as Differentiation

### 2025-07-10 main/conclusion.tex
Some blurb on inductive/coinductive types.

For expedience, lists are the only recursive data type in our source language, so important future work is
supporting general inductive and coinductive types. \citet{nunes2023} support automatic differentiation for
datatypes defined as the least or greatest fixed points of $\mu\nu$-polynomial functors; we could potentially
adopt a similar approach. Full inductive types would allow us to embed an interpreter for untyped lambda
calculus; combined with the CBN monadic translation described in \secref{todo} which uniformly inserts
approximation points, we should be able to obtain the program slicing behaviour of earlier \GPS work ``for
free''. Coinductive types (e.g.~streams) present additional challenges, especially for defining
join-preserving backward maps, but also open the door to slicing (finite prefixes of) infinite data sources,
with some likely relationship to the problem of dealing with partial or non-terminating computations.

>>>>

Lists are the only recursive data type we provided in our source language, so important future work is
supporting general inductive and coinductive types. \citet{nunes2023} support automatic differentiation for
datatypes defined as the least or greatest fixed points of $\mu\nu$-polynomial functors; we could potentially
adopt a similar approach. Full inductive types would allow us to embed an interpreter for untyped lambda
calculus; combined with the CBN monadic translation described in \secref{todo} which uniformly inserts
approximation points, we should be able to obtain the program slicing behaviour of earlier \GPS work ``for
free''. Coinductive types (e.g.~streams) present additional challenges, especially for defining
join-preserving backward maps, but also open the door to slicing (finite prefixes of) infinite data sources,
with some likely relationship to the problem of dealing with partial or non-terminating computations.
